\documentclass[11pt,a4paper]{article}
\usepackage{hyperref}

\begin{document}
\title{Treacherous Talks -
  Sprint 3: ``Play a Basic Game''}
\date{\today}
\author{Spokesperson: stephan.brandauer@gmail.com}
\maketitle

\section{The Sprint}
\subsection{Plan ..}
The goal was to ``play a basic game'' which, for us, meant to be able to accept
and execute movement orders through the three interfaces. Scaling, exactness of
rules and the like were not goal of this sprint. We also did not include
graphical visualisation of the game state in our sprint goal, since the visual
properties of the system do not matter much to our customer.

\subsection{.. and Reality}
We managed to fulfill the sprint goal and even pulled in more stories from
the back log, this is why we chose to increase the focus factor for sprint \#4 a
bit. Big improvements were the significant reduction of build time during 
sprint \#3 and the fix of the release system. We are now able to directly use
the releases from our Continuous Integration system.
The team agrees that this sprint went very well.

\subsection{The Stories}
\begin{tabular}{l|c}
Create poster for the EUC & done \\
Unix school & done \\
Refactor UIs & done \\
Rule Engine & done \\
Setup game as an organizer & done \\
Get an overview of a game & done \\
Join games & done \\
Implement game application logic & done \\
Make game plays & done \\
\end{tabular}

\newpage
\subsection{Retrospective}
\subsubsection*{What should be done differently:}
\begin{itemize}
\item Better Demo Preparation
\item Independent Tasks/Stories
\item Document Code Better
\end{itemize}

In general, the team is very happy about the progress we are making, although
there is a lack of customer feedback at the moment which we will hopefully
resolve this week.

\end{document}
